\begin{thebibliography}{99}
    \bibitem{1} M. Martini, et al., "A surveillance system for diseases of companion animals in the Veneto region(Italy)," Scientific
    and Technical Review of the Office International des Epizooties, vol. 36, no. 3, pp. 1007-1014, 2017.

   \bibitem{2} Nilesh Kulkarni, "Support vector machine based alzheimer's disease diagnosis using synchrony features," International Journal of Informatics and Communication Technology, vol. 9, no. 1, pp. 57-62, 2020.
   
    \bibitem{3} V. M. Nisha and L. Jeganathan, "A symmetry based anomaly detection in brain using cellular automata for computer
    aided diagnosis," Indonesian Journal of Electrical Engineering and Computer Science, vol. 14, no. 1, pp. 471-477, 2019.
   
   \bibitem{4} M. Y. Munirah, et al., "Design and development of online dog diseases diagnosing system," International Journal of Information and Education Technology, vol. 6, no. 11, pp. 913-916, 2016.

   \bibitem{5} H. Qin, et al., "Horse-Expert: An aided expert system for diagnosing horse diseases," Polish journal of veterinary sciences, vol. 19, no. 4, pp. 907-915, 2016.

   \bibitem{6} L. Rong and D. Li, "A web based expert system for milch cow disease diagnosis system in China," International Conference on Computer and Computing Technologies in Agriculture, Springer US, pp. 1441-1445, 2007.

   \bibitem{7} A. Nugroho, et al., "Mobile expert system using fuzzy tsukamoto for diagnosing cattle disease," Procedia computer science, vol. 116, pp. 27-36, 2017.

   \bibitem{8} Z. Ráduly, C. Sulyok, Z. Vadászi, and A. Zölde, "Dog Breed 
    Identification Using DeepLearning," 2018 IEEE 16th International Symposium on
    Intelligent Systems and Informatics (SISY), 2018, pp. 000271-000276, doi:10.1109/SISY.2018.8524715. 
    
   \bibitem{9} M. V. SaiRishita and T. Ahmed Harris, "Dog Breed Classifier using Convolutional Neural Networks," 2018 International Conference on
    Networking, Embedded and Wireless Systems (ICNEWS), 2018, pp.1-7, doi:10.1109/ICNEWS.2018.8903980.

 
   \bibitem{10} Kumar, M., Yadav, D. K., Singh, A., \& Gupta, V. K. (2015). A movie recommender system: Movrec. International journal of computer applications, 124(3), 7-11. 
   
   \bibitem{11} Virk, H. K., Singh, E. M., \& Singh, A. (2015). Analysis and design of hybrid online movie recommender system. International journal of innovations in engineering and technology (IJIET), 5(2), 159-163.

   \bibitem{12} De Campos, L. M., Fernández-Luna, J. M., Huete, J. F., \& Rueda-Morales, M. A. (2010). Combining content-based and collaborative recommendations: a hybrid approach based on Bayesian networks. International journal of approximate reasoning, 51(7), 785-799.
   
   \bibitem{13} Kuzelewska, U. (2014). Clustering algorithms in hybrid recommender system on movielens data. Studies in logic, grammar and rhetoric, 37(1), 125-139.

   \bibitem{14} Burd, B. (2020) in Flutter. Hoboken, NJ: For Dummies.    
   \bibitem{15} Oswald, A. (2016) in Dart. London: Faber Members. 
   \bibitem{16} Momjian, B. (2001) in PostgresSQL: Introduction and concepts. Boston ... et al.: Addison-Wesley. 
   \bibitem{17} Cheung, V. (2021) in Neon. North Point, Hong Kong: Viction:ary. 
   \bibitem{18} LUBANOVIC, B. (2022) in Python. S.l.: DE BOECK SUPERIEUR. 
   \bibitem{19} Zeiger, J. (2012) Pandas. New York: Children's Press. 
   \bibitem{20} Garreta, R. et al. (2017) in Scikit-Learn: Machine Learning Simplified. Birmingham, UK: Packt Publishing. 
   \bibitem{21} Mueller, J. and Massaron, L. (2019) in Deep learning for dummies. Hoboken, NJ: John Wiley \& Sons, Inc. 
   \bibitem{22} \url{https://www.researchgate.net/publication/338603223/figure/fig1/AS:847598516711425@1579094642237/ResNet-50-architecture-26-shown-with-the-residual-units-the-size-of-the-filters-and.png}
   \bibitem{23} Lieberman, H. (1995). Letizia: An Agent that Assists Web Browsing. In
    Proceedings of the 1995 International Joint Conference on Artificial Intelligence. Montreal,
    Canada.
    \bibitem{24} Pazzani, M., Muramatsu, J. and Billsus, D. (1996). Syskill \& Webert: Identifying
    interesting web sites. In Proceedings of the Thirteenth National Conference on Artificial
    Intelligence AAAI 96, pp. 54-61.
    \bibitem{25} Jennings, A. and Higuchi, H. (1992). A Personal News Service based on a
    User Model Neural Network. IEICE Transactions on Information and Systems, Vol. E75-D, No. 2,
    pp. 198-209.
\end{thebibliography}
\bibliographystyle{plain}