
\section{FUTURE ENHANCEMENT}
\textbf{Shop Features and E-commerce Integration}\\
Expand the shop section by collaborating with pet product brands and introducing a wider range of products.
Implement an intelligent recommendation system for pet products based on the user's pet profile and preferences.

\noindent\textbf{Pet Fitness and Activity Tracking}\\
Integrate fitness tracking features, such as step counting and activity monitoring, to encourage pet owners to keep their pets active and healthy.
Provide insights into the daily exercise needs of specific breeds and offer personalized activity goals.

% \textbf{Augmented Reality (AR) Features}\\
%     Explore the integration of AR for virtual pet try-ons, allowing users to visualize how certain pet products or accessories will look on their specific breed.
%     Implement AR-based training simulations or interactive features for users to engage with their pets in a virtual environment.

\noindent\textbf{Education and Training Modules}\\
Develop interactive modules within the app to educate pet owners on specific breed characteristics, training tips, and common health issues.
Integrate virtual training sessions or challenges to enhance the bond between pets and owners.

\noindent\textbf{Integration with Veterinary Services}\\
Collaborate with veterinary services to offer telemedicine consultations or appointment scheduling through the app.
Implement a feature for users to store and manage their pet's medical records securely.

% \textbf{Personalized Alerts and Notifications}\\
%     Enhance the app's notification system to provide timely reminders for vaccinations, grooming sessions, and other important pet-related activities.
%     Implement AI-driven alerts for potential health issues based on the pet's history and behavior patterns.

\noindent\textbf{Internationalization and Multilingual Support}\\
Expand the app's reach by adding support for multiple languages to cater to a global audience.
Consider incorporating location-specific information and services for users in different regions.